---
output:
  html_document: default
  word_document: default
---
load relevant libraries
load packages
```{r include=FALSE}
rm(list=ls())

#if(!require(installr)) {
#  install.packages("installr"); 
#  require(installr)
#} #load

#updateR()


if(!require("pacman")) install.packages('pacman')
pacman::p_load(NetworkToolbox,
               # graph,
               leidenAlg,
               ggthemes,
               knitr ,
               ResIN,
               data.table,
               igraph,
               qgraph,
               tidyverse,
               dplyr,
               ggplot2,
               naniar,
               gdata,
               doParallel,
               wCorr,
               qgraph,
               MASS,
               Matrix,
               matrixcalc,
               randcorr,
               rWishart,
               ggpubr,
               ggdark )


```

set working directory

```{r include=FALSE}

### MANUAL INPUT: specify and set working directory ###
workdirec <-"C:/Users/20225262/OneDrive - TU Eindhoven/Documents/GitHub/ResIN" 
setwd(workdirec)
source("functions_behaviorspace_table_output_handling.R")

### MANUAL INPUT: Optionally specify filepath (i.e. where the behaviorspace csv is situated) ###
#NOTE: if csv files are placed in the workdirec, then leave filesPath unchanged
filesPath <- ""
### MANUAL INPUT: specify filenames ###
filesNames <- c(
  "C:/Users/20225262/OneDrive - TU Eindhoven/Documents/Courses/ResIN/Resin dummy experiment.csv"
  )


```


Read data and rename columns
```{r include=FALSE}
# READ DATA ---------------------------------------------------------------

df <- loadData(filesPath, filesNames)


# REMOVE IRRELEVANT VARIABLES ---------------------------------------------------------------

df <- removeVariables(df)

# RENAME VARIABLES ---------------------------------------------------------------
printColumnNames(df)

  ### MANUAL INPUT: specify new (easy-to-work-with) variable names ###
  new_variable_names <- list(
    "run_number",
    "k",
   # "levels",
  #  "items", 
   # "ordinality",
    "Population_Size",
    "Degree_of_Cognition", 
    "seed",
    "time_step",
    "adjacency_matrix",
    "IC_Global",
    "IC_Neighbors"
  )

#change variable names
variable_names <- names(df)
if (length(variable_names) == length(new_variable_names)) {
  clean_df <- changeColumnNames(df, new_variable_names)
} else {
  print (length(variable_names))
  print (length(new_variable_names))
  print("ERROR: the number of variable names you specified is not the same as the number of variables present within the dataframe; please check again")
}
```

Compute Modularity


```{r message=FALSE, warning=FALSE, include=FALSE}
#ComputeModularity <- function(p_clean_df, column_name, levels_stable, items_stable, stable_levels, stable_items, column_levels, column_items, resolution_parameter)
                 #resolution_parameter, add more to to list to compare modularity
ComputeModularity <- function(p_clean_df, column_name, levels_stable, items_stable, stable_levels, stable_items, column_levels, column_items) {
  for(i in 1:length(p_clean_df[[column_name]])) {
    if (levels_stable == "true" && items_stable == "true") {
      columns <- stable_levels * stable_items
    }
    else if (levels_stable == "true" && items_stable == "false"){
      columns <- stable_levels * p_clean_df[[i,column_items]]
    }
    else if (levels_stable == "false" && items_stable == "true"){
      columns <- p_clean_df[[i,column_levels]] * stable_items 
    }
    else {
      columns <- p_clean_df[[i,column_levels]] * p_clean_df[[i,column_items]]
    }
    aj_matrix <- pmax(matrix(scan(quiet = TRUE, text = toString(p_clean_df[[i,column_name]])), ncol = columns,byrow = TRUE),0)
    colnames(aj_matrix) <- paste("Column", seq(ncol(aj_matrix)))
    aj_graph <- igraph::graph_from_adjacency_matrix(aj_matrix, mode = "undirected", weighted = TRUE, diag = FALSE)
    
    cluster <- cluster_leiden(aj_graph, resolution_parameter = 0.4, objective_function = "modularity", n_iterations = 10)
    # cluster <- cluster_walktrap(ResIN_igraph)
    #  cluster <- cluster_leading_eigen(ResIN_igraph)
    #   cluster <- cluster_louvain(ResIN_igraph)
    #   cluster <- cluster_fast_greedy(ResIN_igraph)
    #    cluster <- cluster_spinglass(ResIN_igraph)
    #   cluster <- cluster_fluid_communities((ResIN_igraph))
    communities <- igraph::membership(cluster)
    nodes <- names(communities)
    outcome <- as.data.frame(cbind(as.numeric(communities), nodes))
    colnames(outcome) <- c("cluster", "from")
      outcome$cluster <- as.integer(outcome$cluster)
    remove <- c()
    cluster_list <- outcome$cluster

    x <- length(unique(outcome$cluster))
    i <- 1

    remove <- c()
        while(i <= x) {
      if(length(outcome$cluster[outcome$cluster==i]) < 2) {
        remove <- append(remove, as.numeric(outcome$cluster[outcome$cluster==i]))
        outcome$cluster[outcome$cluster==i] <- rep("NA", length(outcome$cluster[outcome$cluster==i]))
      }
      i <- i+1}
     clusters <- length(unique(as.numeric(outcome$cluster[outcome$cluster !="NA"] )))
     
   
     remove_list <- which(cluster_list %in% remove)
     index <- 0
     aj_matrix2 <- aj_matrix
     if (length(remove_list) > 0) {
       for (i in remove_list[order(remove_list)]) {
       i <- i - index
       aj_matrix2 <- aj_matrix2[-c(as.numeric(i)), -c(as.numeric(i))]
       index <- index + 1
}
   
   
    aj_graph2 <-  igraph::graph_from_adjacency_matrix(aj_matrix2, mode = "undirected", weighted = TRUE, diag = FALSE)
    cluster2 <- cluster_leiden(aj_graph2, resolution_parameter = 0.4, objective_function = "modularity", n_iterations = 10)
    communities2 <- igraph::membership(cluster2)
    
    md <- modularity(aj_graph2, communities2)
     } else {
     md <- modularity(aj_graph, communities)
     }
    if (exists('md_df') && is.data.frame(get('md_df'))) {
      md_df <- rbind(md_df, md)
      clusters_df <- rbind(clusters_df, clusters)
      removed_df <- rbind(removed_df, length(remove_list))
    }
    else {
      md_df <- data.frame(md)
      clusters_df <- data.frame(clusters)
      removed_df <- data.frame(length(remove_list))
    }
  }
    p_clean_df <- cbind(p_clean_df, md_df)
    colnames(p_clean_df)[ncol(p_clean_df)] = paste("Modularity" )
    p_clean_df <- cbind(p_clean_df, clusters_df)
    colnames(p_clean_df)[ncol(p_clean_df)] = paste("Clusters" )
    p_clean_df <- cbind(p_clean_df, removed_df)
    colnames(p_clean_df)[ncol(p_clean_df)] = paste("Isolated_Nodes" )
    rm(list = ls(p_clean_df))
  return (p_clean_df)
}





df_mod <- clean_df
df_mod <- ComputeModularity(df_mod, 7, "true", "true", 5, 7,4,5)
#kable(df_mod<- subset(df_mod, select = -c(adjacency_matrix)), format = "html", booktabs = TRUE)


```



Transform variables with right label
```{r include=FALSE}
#transform 'measurement' variable to numeric (as to avoid ggplot errors)
df_mod$Modularity <- as.numeric(df_mod$Modularity)
df_mod$Clusters <- as.numeric(df_mod$Clusters)
df_mod$Isolated_Nodes <- as.numeric(df_mod$Isolated_Nodes)
#round 'measurement' variable to 4 decimals
df_mod$Modularity <- round(df_mod$Modularity, 4)
#convert categorical variables to factors (as to avoid ggplot errors)
df_mod$run_number <- as.integer(df_mod$run_number)
df_mod$k <- as.factor(df_mod$k)
df_mod$Degree_of_Cognition <- as.factor(df_mod$Degree_of_Cognition)
df_mod$Population_Size <- as.factor(df_mod$Population_Size)
df_mod$seed <- as.factor(df_mod$seed)


```


Make Graphs
---------------------------------
Modularity

```{r echo=FALSE, fig.height=7.5, fig.width=7.5, message=FALSE, warning=FALSE, results='asis'}
    
df_mod %>% 
   ggplot(aes(x = time_step,
                y = Modularity)) +
    
    geom_smooth(aes(group=k, color=k),
                method="loess", formula = 'y ~ x', size=1.4, span = 0.2, se=F, fullrange=FALSE, level=0.95) +
    xlab("Timesteps") +
    ylab("Modularity") + 
    labs(title = "Evolution of Modularity (Leiden_algorithm , resolution-parameter == 0.4)",
       subtitle = "Items == 5, Levels == 7, repetitions == 5 ")+
    scale_color_viridis_d()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 15), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 15) ) +
      facet_grid(Degree_of_Cognition ~ Population_Size , labeller = label_both ) 



```
Clusters

```{r echo=FALSE, fig.height=7.5, fig.width=7.5, message=FALSE, warning=FALSE, results='asis'}
    
df_mod %>% 
ggplot(aes(x = time_step,
                y = Clusters)) +
    
    geom_smooth(aes(group=k, color=k),
                method="loess", formula = 'y ~ x', size=1.4, span = 0.2, se=F, fullrange=FALSE, level=0.95) +
    xlab("Timesteps") +
    ylab("Clusters") + 
    labs(title = "Evolution of Clusters (Leiden Algoritm, resolution-parameter == 0.4)",
       subtitle = "Items == 5, Levels == 7, repetitions == 5 ")+
    scale_color_viridis_d()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 15), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 15) ) +
     facet_grid(Degree_of_Cognition ~ Population_Size , labeller = label_both )  



```

Isolated Nodes


```{r echo=FALSE, fig.height=7.5, fig.width=7.5, message=FALSE, warning=FALSE, results='asis'}
    
df_mod %>% 
ggplot(aes(x = time_step,
                y = Isolated_Nodes)) +
    
    geom_smooth(aes(group=k, color=k),
                method="loess", formula = 'y ~ x', size=1.4, span = 0.2, se=F, fullrange=FALSE, level=0.95) +
    xlab("Timesteps") +
    ylab("Isolated Nodes") + 
    labs(title = "Evolution of Isolated Nodes (Leiden Algoritm, resolution-parameter == 0.4)",
       subtitle = "Items == 5, Levels == 7, repetitions == 5 ")+
    scale_color_viridis_d()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 15), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 15) ) +
     facet_grid(Degree_of_Cognition ~ Population_Size , labeller = label_both )  



```
Internal Coherence Whole World Scenario

```{r echo=FALSE, fig.height=7.5, fig.width=7.5, message=FALSE, warning=FALSE, results='asis'}
    
df_long <- dplyr::select(clean_df, -adjacency_matrix)
df_long <- gather(df_long, variable, measurement, IC_Global:IC_Neighbors)

# SPECIFY VARIABLE MEASUREMENT SCALES -----------------------------------------------------
### MANUAL INPUT: in order for ggplot and plotly to work, one must specify the following: ###
#-> continuous decimal (floating) variables as 'numeric'
#-> continuous integer variables as 'integer'
#-> discrete (or categorical) variables as 'factor'

#print an overview of variables and their measurement scales
str(df_long)
#transform 'measurement' variable to numeric (as to avoid ggplot errors)
df_long$measurement <- as.numeric(df_long$measurement)
#round 'measurement' variable to 4 decimals
df_long$measurement <- round(df_long$measurement, 4)
#convert categorical variables to factors (as to avoid ggplot errors)
df_long$run_number <- as.integer(df_long$run_number)
df_long$variable <- as.factor(df_long$variable)



```

Internal Coherence ------- Whole World Scenario

```{r echo=FALSE, fig.height=7.5, fig.width=7.5, message=FALSE, warning=FALSE, results='asis'}
df_long %>% filter(Degree_of_Cognition == "whole-world") %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = time_step,
                y = measurement)) +
    
    geom_smooth(aes(group=k, color=k),
                method="loess", formula = 'y ~ x', size=1.4, span = 0.2, se=F, fullrange=FALSE, level=0.95) +
    xlab("Timesteps") +
    ylab("Mean Internal Coherence") + 
    labs(title = "Evolution of Mean Internal Coherence (Degree_of_Cognition == Whole World)",
       subtitle = "Items == 5, Levels == 7, repetitions == 5 ")+
    scale_color_viridis_c()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 14), 
          plot.subtitle = element_text( size = 14),
          axis.title = element_text( size = 14) ) +
     facet_grid(~Population_Size , labeller = label_both )  



```
Internal Coherence ---- Neighbors scenario

```{r echo=FALSE, fig.height=7.5, fig.width=7.5, message=FALSE, warning=FALSE, results='asis'}
df_long %>% filter(Degree_of_Cognition == "neighbors") %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = time_step,
                y = measurement)) +
    
    geom_smooth(aes(group=k, color=k),
                method="loess", formula = 'y ~ x', size=1.4, span = 0.2, se=F, fullrange=FALSE, level=0.95) +
    xlab("Timesteps") +
    ylab("Mean Internal Coherence") + 
    labs(title = "Evolution of Mean Internal Coherence (Degree_of_Cognition == Neighbors)",
       subtitle = "Items == 5, Levels == 7, repetitions == 5 ")+
    scale_color_viridis_c()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 14), 
          plot.subtitle = element_text( size = 14),
          axis.title = element_text( size = 14) ) +
     facet_grid(variable ~ Population_Size, labeller = label_both )  



```



Evolution Response Network for k == 2, Degree of Cognition == whole-world, resolution parameter leiden algoritm = 0.4



```{r echo=FALSE, fig.height=7.5, fig.width=7.5, message=FALSE, warning=FALSE, results='asis'}



# Compute Adjacency Matrix --------------------------------------------------------------
ComputeAM <- function(p_clean_df, stable_levels, stable_items) {
    columns <- stable_levels * stable_items
    aj_matrix <- pmax(matrix(scan(quiet = TRUE, text = toString(p_clean_df)), ncol = columns,byrow = TRUE),0)
    colnames(aj_matrix) <- paste("Column", seq(ncol(aj_matrix)))
  index1 <- 1
  index2 <- 1 
  
  
  for (i in 1:ncol(aj_matrix)) {
    colnames(aj_matrix)[[i]] = paste0(index1, sep = "_", index2 ) 
    index2 <- index2 + 1 
    if ((index2) > stable_levels ) {
      index1 <- index1 + 1
      index2 <- 1
}
  }
  return(aj_matrix)
}

 plot_time_steps <- list( 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90, 95, 100, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 200, 250, 300, 350, 400, 450, 500)
 plot_list <- list()
for (z in plot_time_steps) {
  
 


selected_df <- df_mod %>% 
   filter(run_number == 85
          , time_step == z)
resin_adj <- ComputeAM(selected_df[1,7], 7, 5)

## Generating the qgraph and igraph objects

ResIN_igraph <- igraph::graph_from_adjacency_matrix(resin_adj, mode = "undirected", weighted = TRUE, diag = FALSE)
ResIN_qgraph <- qgraph::qgraph(resin_adj, DoNotPlot = TRUE, layout = "spring")

graph_layout <- as.data.frame(prcomp(igraph::layout_with_fr(ResIN_igraph))$x)
graph_layout$node_names <- colnames(resin_adj)
colnames(graph_layout) <- c("x", "y", "node_names")

node_frame <- graph_layout
node_frame$from <- node_frame$node_names

## Perform clustering analysis
cluster = TRUE
  if(cluster==TRUE) {
    cluster <- cluster_leiden(ResIN_igraph, resolution_parameter = 0.4, objective_function = "modularity", n_iterations = 10)
  # cluster <- cluster_walktrap(ResIN_igraph)
    #  cluster <- cluster_leading_eigen(ResIN_igraph)
 #   cluster <- cluster_louvain(ResIN_igraph)
 #   cluster <- cluster_fast_greedy(ResIN_igraph)
#    cluster <- cluster_spinglass(ResIN_igraph)
#   cluster <- cluster_fluid_communities((ResIN_igraph))
    communities <- igraph::membership(cluster)
    nodes <- names(communities)
    outcome <- as.data.frame(cbind(as.numeric(communities), nodes))
    colnames(outcome) <- c("cluster", "from")
    outcome$cluster <- as.numeric(outcome$cluster)


    x <- length(unique(outcome$cluster))
    i <- 1

        while(i <= x) {
      if(length(outcome$cluster[outcome$cluster==i]) < 2) {
        outcome$cluster[outcome$cluster==i] <- rep("NA", length(outcome$cluster[outcome$cluster==i]))
      }
      i <- i+1}
     clusters <- length(unique(as.numeric(outcome$cluster[outcome$cluster !="NA"] )))
     
   
    
     index <- 0
     

    outcome$cluster[outcome$cluster=="NA"] <- NA
    outcome$cluster <- as.numeric(outcome$cluster)
    node_frame <- dplyr::left_join(node_frame, outcome, by = "from")
  }

## Preparing plotting data for ggplot graph format
g <- igraph::as_data_frame(ResIN_igraph)
g$from.x <- node_frame$x[match(g$from, node_frame$node_names)]
g$from.y <- node_frame$y[match(g$from, node_frame$node_names)]
g$to.x <- node_frame$x[match(g$to, node_frame$node_names)]
g$to.y <- node_frame$y[match(g$to, node_frame$node_names)]

edgelist_frame <- dplyr::left_join(g, node_frame, by = "from")

edge_plot_i <- ggplot() +
    geom_curve(data = edgelist_frame, aes(x = from.x, xend = to.x, y = from.y,
                yend = to.y, size = weight^5), curvature = 0.15, color = "darkgrey", alpha = 0.8) +
   geom_label(data = node_frame, aes(x = x, y = y, label = node_names, color = as.factor(cluster)), size = 5)+
#    geom_label(data = edgelist_frame, aes(x = from.x, y = from.y, label = from, color = as.factor(cluster)), size = 5) +
  #  geom_label(data = edgelist_frame, aes(x = to.x, y = to.y, label = to, color = as.factor(cluster)), size = 5) +
                  ## Make sure to plot node labels both based on the to and from columns in the plotting frame
    ggtitle(z)+
    labs(color = "Clusters: ")+
    scale_size_continuous(guide = "none")+
    theme_bw()+
    theme(axis.text.x = element_blank(), axis.title.x = element_blank(),
          axis.text.y = element_blank(), axis.title.y = element_blank(),
          axis.ticks = element_blank(), panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(), legend.position = "bottom",
          legend.text = element_blank(), plot.title = element_text(hjust = 0.5, size=18))
plot_list <- append(plot_list, edge_plot_i)
plot(edge_plot_i)
}

```

