---
output:
  html_document: default
  pdf_document: default
  word_document: default
---


```{r include=FALSE}
#load relevant libraries
#load packages

rm(list=ls())

if(!require(installr)) {
  install.packages("installr"); 
  require(installr)
} #load

#updateR()


if(!require("pacman")) install.packages('pacman')
pacman::p_load(NetworkToolbox,
               # graph,
               leidenAlg,
               ggthemes,
               knitr ,
               see,
               scico,
               data.table,
               igraph,
               qgraph,
               tidyverse,
               dplyr,
               ggplot2,
               naniar,
               gdata,
               doParallel,
               wCorr,
               qgraph,
               MASS,
               Matrix,
               matrixcalc,
               randcorr,
               rWishart,
               devtools,
               ggpubr,
               tinytex,
               ggdark )

```

##set working directory

```{r include=FALSE}

### MANUAL INPUT: specify and set working directory ###
workdirec <-"C:/Users/20225262/OneDrive - TU Eindhoven/Documents/GitHub/Testing-Modules-of-Social-Tipping" 


setwd(workdirec)
source("functions_behaviorspace_table_output_handling.R")

### MANUAL INPUT: Optionally specify filepath (i.e. where the behaviorspace csv is situated) ###
#NOTE: if csv files are placed in the workdirec, then leave filesPath unchanged
filesPath <- "C:/Users/20225262/OneDrive - TU Eindhoven/Documents/Models/Social Tipping Modules/Probalistic/"
### MANUAL INPUT: specify filenames ###

#filesPathPatterns <- list("Experiment1DR*","Experiment3DR*","Experiment7DR*")


#filesNames <- list.files(path = filesPath, pattern = "")
# READ DATA ---------------------------------------------------------------

#df2 <- loadData(filesPath, filesNames)
#df2 <- removeVariables(df2)

```

``` {r include = FALSE}

# REMOVE IRRELEVANT VARIABLES ---------------------------------------------------------------


# RENAME VARIABLES ---------------------------------------------------------------
printColumnNames(df3)

  ### MANUAL INPUT: specify new (easy-to-work-with) variable names ###
  new_variable_names <- list(
    "Run_Number",
    "Dekkers_Power",
    "Node_Degree",
     "Tipping_Strategy",
      "Communities",
     "Rewiring_Proportion",
   # "duration_to_decision",
   #  "Population_Size",
      "Clustering_Exponent",
      "Innovators",
      "ticks",
   # "MSCe",
  #  "MEC",
  #  "MBC",
  #  "MCCe",
   "MSCl",
    "GCC",
    "MCPL",
    "MPL",
  #   "VCCe",
  #  "VEC",
  #  "VBC",
    "VCCo",
   "VD",
#    "Majority_Green",
   "Green_Percentage",
    "Sim_Time"
    )

#change variable names
variable_names <- names(df3)
if (length(variable_names) == length(new_variable_names)) {
  clean_df <- changeColumnNames(df3, new_variable_names)
} else {
  print (length(variable_names))
  print (length(new_variable_names))
  print("ERROR: the number of variable names you specified is not the same as the number of variables present within the dataframe; please check again")
}

#clean_df <- subset(clean_df, Tipping_Strategy != "Shotgun-NS")


#clean_df <- clean_df[!(clean_df$Mean_Path_Length %in% "false"),]

#clean_df <- clean_df[order(clean_df$Run_Number),]


```

```{r include=false}
#df1 <- add_column(df1, dekkers.power = 5, .after = 1 )
#df1 <- subset( df1, select = -dekkers.power.1 )
#df3 <- dplyr::bind_rows(df1, df2)
#write.csv(clean_df,"C:/Users/20225262/OneDrive - TU Eindhoven/Documents/Models/Social Tipping Modules/Probalistic/Probs_clean.csv" )
#write.csv(df_mean,"C:/Users/20225262/OneDrive - TU Eindhoven/Documents/Models/Social Tipping Modules/Probalistic/Probs_mean_clean.csv" )
#clean_df<- filter(clean_df, clean_df$Tipping_Strategy != "S_Closeness")
#clean_df<- clean_df %>% mutate(across(c('Green_Percentage'), round,0))
#df_mean <-  clean_df %>%
# group_by(Dekkers_Power, Tipping_Strategy, Innovators, Communities, Node_Degree, Rewiring_Proportion, Clustering_Exponent) %>%
#  summarise_if(is.numeric, mean, na.rm = TRUE)
```

``` {r include = FALSE}

# REMOVE IRRELEVANT VARIABLES ---------------------------------------------------------------

df <- read.csv("C:/Users/20225262/OneDrive - TU Eindhoven/Documents/Models/Social Tipping Modules/Probalistic/Probs_clean.csv", header = TRUE)
df_mean <- read.csv("C:/Users/20225262/OneDrive - TU Eindhoven/Documents/Models/Social Tipping Modules/Probalistic/Probs_mean_clean.csv", header = TRUE)

df <- df[-c(1)]
df_mean <-  df_mean[-c(1)]

#printColumnNames(df)
  ### MANUAL INPUT: specify new (easy-to-work-with) variable names ###
  new_variable_names <- list(
   "Run_Number",
    "Dekkers_Power",
    "Node_Degree",
     "Tipping_Strategy",
      "Communities",
     "Rewiring_Proportion",
   # "duration_to_decision",
   #  "Population_Size",
      "Clustering_Exponent",
      "Innovators",
      "ticks",
   # "MSCe",
  #  "MEC",
  #  "MBC",
  #  "MCCe",
   "MSCl",
    "GCC",
    "MCPL",
    "MPL",
  #   "VCCe",
  #  "VEC",
  #  "VBC",
    "VCCo",
   "VD",
#    "Majority_Green",
   "Green_Percentage",
    "Sim_Time"
    )

#change variable names
#clean_df <- changeColumnNames(df, new_variable_names)
#new_variable_names <- append(new_variable_names, "IO_Ratio_N")
#df_mean <- changeColumnNames(df_mean, new_variable_names)

clean_df <- df
```

```{r include=FALSE}
#df_mean$Innovators <- as.numeric(df_mean$Innovators)
#df_mean$Innovators <- df_mean$Innovators / 10 
#df_mean$Green_Percentage <- as.numeric(df_mean$Green_Percentage)
#df_mean <- df_mean %>% mutate(IO_Ratio_N = Green_Percentage / Innovators)

#df_mean <- df_mean %>% mutate(IO_Ratio_O = cut(df_mean$IO_Ratio_N, breaks=c(0, 0.5, 0.75, 1, 1.25,1.5, Inf)))
  
```

##Transform variables with right label
```{r include=FALSE}
#transform 'measurement' variable to numeric (as to avoid ggplot errors)
#clean_df$NCSAG <- as.numeric(clean_df$NCSAG)
#clean_df$NCSAB <- as.numeric(clean_df$NCSAB)
clean_df$Sim_Time <- as.numeric(clean_df$Sim_Time)


clean_df$Node_Degree <- as.factor(clean_df$Node_Degree)
#clean_df$Mean_Cluster_Coefficient <- as.factor(clean_df$Mean_Cluster_Coefficient)
#clean_df$Majority_Green <- as.numeric(clean_df$Majority_Green)
clean_df$Dekkers_Power <- as.factor(clean_df$Dekkers_Power)
#clean_df$duration_to_decision <- as.factor(clean_df$duration_to_decision)
clean_df$Rewiring_Proportion<- as.factor(clean_df$Rewiring_Proportion)
#clean_df$Stop_Time <- as.factor(clean_df$Stop_Time)
#clean_df$Population_Size <- as.factor(clean_df$Population_Size)
df_mean$Innovators <- as.factor(df_mean$Innovators)
clean_df$Innovators <- as.factor(clean_df$Innovators)
clean_df$Tipping_Strategy<- as.factor(clean_df$Tipping_Strategy)
#clean_df$Communities<- as.factor(clean_df$Communities)
#clean_df$Clustering_Coefficient<- as.factor(clean_df$Clustering_Coefficient)
df_mean$IO_Ratio_N <- as.numeric(df_mean$IO_Ratio_N)



```


##Make Graphs
--------------------------------- Mean Simple Path Length
```{r echo=FALSE,fig.height=15, fig.width=15, message=TRUE, warning=TRUE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
#install.packages("see")
#ibrary(see)
clean_df$Rewiring_Proportion <- as.factor(clean_df$Rewiring_Proportion)
df_long <- clean_df  %>% gather( variable, measurement, ticks:Sim_Time) %>% filter( Tipping_Strategy != "S_Closeness")
output_parameters <- list("MPL", "MCPL", "MSCl", "VCCo", "VD")
out_para_names <- list("Mean_Shortest_Path_Length", "Mean_Complex_Path_Length", "Mean_Cluster_Coefficient", "Variance_Cluster_Coefficient", "Variance_Node_Degree")

compute_plot <- function(k, i) {
df_use <- df_long %>% filter(variable == k, Node_Degree == 7) %>%
   dplyr::sample_frac()
g_plot <- ggplot(df_use, aes(x = measurement, y = Clustering_Exponent, color = Rewiring_Proportion )) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   #geom_smooth(span=0.8)+
    xlab(i) +
    ylab("Clustering_Exponent") + 
   labs(title = "Node Degree == 10")+
    scale_color_oi()+ 
   # scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid(Communities~ Dekkers_Power, labeller = label_both )
print(g_plot)
}
for (i in 1:length(output_parameters)){
  compute_plot(output_parameters[[i]],out_para_names[i])
}

```

```{r echo=FALSE,fig.height=15, fig.width=15, message=TRUE, warning=TRUE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"

clean_df$Rewiring_Proportion <- as.factor(clean_df$Rewiring_Proportion)
#df_long <- clean_df  %>% gather( variable, measurement, ticks:Sim_Time) %>% filter( Tipping_Strategy != "S_Closeness")
output_parameters <- list(4, 7, 10)
out_para_names <- list("Node Degree == 4", "Node Degree == 7", "Node Degree == 10")
output_p2 <- list("MPL", "MCPL", "MSCl", "GCC", "VCCo", "VD")
out_p2_names <- list("Mean_Shortest_Path_Length", "Mean_Complex_Path_Length", "Mean_Cluster_Coefficient", "Global_Clustering_Coefficient", "Variance_Cluster_Coefficient", "Variance_Node_Degree")

compute_plot_nw <- function(k,i,l,j) {
df_use <- filter(clean_df,clean_df$Node_Degree == k)
df_use_mean <- filter(df_mean, df_mean$Node_Degree == k)
p <-as.name(l)
g_plot <- ggplot() +
    #geom_histogram(binwidth=0.01)+
  #    geom_point(data=df_use, aes(x = IO_Ratio_N, y =MPL, color = Tipping_Strategy ), size = 1) + 
   geom_point(data=df_use_mean, aes(x = !!ensym(p), y = Green_Percentage, color = Tipping_Strategy), size =1) + 
  geom_smooth(data=df_use_mean, aes(x = !!ensym(p), y = Green_Percentage, color = Tipping_Strategy), span=0.8)+
    xlab(j) +
    ylab("Ratio Adopted") +
   labs(title = "Probabilisic")+
 # scico::scale_color_scico(palette = "lajolla")+
    scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
           # panel.background = element_rect(fill = "beige"),
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid(~Innovators, labeller = label_both )
# ggnewscale::new_scale_color() +
#  geom_point(data=df_use_mean, aes(x = MPL, y = MSCl, color = Majority_Green), size = 2) +
 #  scale_color_brewer(,,palette = "Blues")
 ggsave(g_plot, file=paste0("mean_",i,l,".png"), width = 10, height = 10, units = "in")
#print(g_plot)

}
for (i in 1:length(output_parameters)){
  for (k in 1:length(output_p2)) {
  compute_plot_nw(output_parameters[[i]],out_para_names[i], output_p2[[k]], out_p2_names[k])
  }
}
```


```{r echo=FALSE,fig.height=15, fig.width=15, message=TRUE, warning=TRUE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"

clean_df$Rewiring_Proportion <- as.factor(clean_df$Rewiring_Proportion)
#df_long <- clean_df  %>% gather( variable, measurement, ticks:Sim_Time) %>% filter( Tipping_Strategy != "S_Closeness")
output_parameters <- list(4, 7, 10)
out_para_names <- list("Node Degree == 4", "Node Degree == 7", "Node Degree == 10")

compute_plot_nw <- function(k,i) {
df_use <- filter(clean_df,Node_Degree == 7)
df_use_mean <- filter(df_mean,Node_Degree == 7) 
g_plot <- ggplot() +
    #geom_histogram(binwidth=0.01)+
  #    geom_point(data=df_use, aes(x = IO_Ratio_N, y =MPL, color = Tipping_Strategy ), size = 1) + 
   geom_point(data=df_use_mean, aes(x = VD, y = IO_Ratio_N, color = Tipping_Strategy), size = 3) + 
  geom_smooth(data=df_use_mean, aes(x = VD, y = IO_Ratio_N, color = Tipping_Strategy), span=0.8)+
    xlab("Mean_Local_Clustering_Coefficient") +
    ylab("Ratio Full Adoption/Seeds") +
   labs(title = i)+
 # scico::scale_color_scico(palette = "lajolla")+
    scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
           # panel.background = element_rect(fill = "beige"),
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid(~Innovators, labeller = label_both )
# ggnewscale::new_scale_color() +
#  geom_point(data=df_use_mean, aes(x = MPL, y = MSCl, color = Majority_Green), size = 2) +
 #  scale_color_brewer(,,palette = "Blues")
print(g_plot)

}
for (i in 1:length(output_parameters)){
  compute_plot_nw(output_parameters[[i]],out_para_names[i])
}

```

##Make Graphs
--------------------------------- Mean Simple Path Length
```{r echo=FALSE,fig.height=15, fig.width=15, message=TRUE, warning=TRUE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"

clean_df$Rewiring_Proportion <- as.factor(clean_df$Rewiring_Proportion)
#df_long <- clean_df  %>% gather( variable, measurement, ticks:Sim_Time) %>% filter( Tipping_Strategy != "S_Closeness")
output_parameters <- list(4, 7, 10)
out_para_names <- list("Node Degree == 4", "Node Degree == 7", "Node Degree == 10")

compute_plot_nw <- function(k,i) {
df_use <- filter(clean_df,Node_Degree == k, Innovators == 0.1)
df_use_mean <- filter(df_mean,Node_Degree == k, Innovators == 0.1) 
g_plot <- ggplot() +
    #geom_histogram(binwidth=0.01)+
  #    geom_point(data=df_use, aes(x = MPL, y =MSCl, color = VD ), size = 1) + 
   geom_point(data=df_use_mean, aes(x =  VD, y = MPL, color = Green_Percentage), size = 3) + 
  #geom_smooth(data=df_use_mean, aes(x = GCC , y MPL= IO_Ratio_N, color = Tipping_Strategy), span=0.8)+
    xlab("Variance Node Degree") +
    ylab("Mean Shortest Path Length") +
   labs(title = i)+
  scico::scale_color_scico(palette = "lajolla")+
    scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
           # panel.background = element_rect(fill = "beige"),
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid(~Tipping_Strategy, labeller = label_both )
# ggnewscale::new_scale_color() +
#  geom_point(data=df_use_mean, aes(x = MPL, y = MSCl, color = Majority_Green), size = 2) +
 #  scale_color_brewer(,,palette = "Blues")
print(g_plot)

}
for (i in 1:length(output_parameters)){
  compute_plot_nw(output_parameters[[i]],out_para_names[i])
}

```




##Make Graphs
--------------------------------- Mean Simple Path Length
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter(Tipping_Strategy != "S_Closeness") %>%
  dplyr::sample_frac(1) %>%
ggplot(aes(x = MPL, y = Majority_Green, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Mean_Simple_Path_Length") +
    ylab("Majority_Green") + 
   #labs(title = "MPL")+
    scale_color_viridis_d(trans = "log")+
 # scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( Node_Degree ~ Innovators, labeller = label_both ) 

```






--------------------------------- Mean Complex Path Length
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter(Tipping_Strategy != "S_Closeness") %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = MCPL, y = Majority_Green, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Mean_Complex_Path_Length") +
    ylab("Majority_Green") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
 # scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( Node_Degree ~ Innovators, labeller = label_both ) 

```


--------------------------------- Variance Node Degree
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = VD, y = Majority_Green, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Variance_Node_Degree") +
    ylab("Majority_Green") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
  scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```


--------------------------------- Mean Local Clustering Coefficient
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = MSCl, y = Majority_Green, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Mean_Local Clustering Coefficient") +
    ylab("Majority_Green") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
 # scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```


--------------------------------- Mean Global Clustering Coefficient
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = GCC, y = Majority_Green, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Global_Clustering_Coefficient") +
    ylab("Majority_Green") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
  #scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```




--------------------------------- Variance Local Clustering Coefficient
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = VCCo, y = Majority_Green, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Variance Local Clustering Coefficient") +
    ylab("Majority_Green") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
  #scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```
Innovators to Outcome Ratio 

--------------------------------- Mean simple path length and Mean Local Clustering Coefficient
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = VD, y = MSCl, shape == IO_Ratio_O, color = IO_Ratio_O)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
  # geom_smooth(span=0.8)+
    xlab("Mean Simple Path Length") +
    ylab("Mean Local Clustering Coefficient") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
  scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid(Tipping_Strategy ~ Innovators, labeller = label_both ) 

```
--------------------------------- Mean Complex path length and Mean Local Clustering Coefficient
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = MCPL, y = MSCl, shape == IO_Ratio_O, color = IO_Ratio_O)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
  # geom_smooth(span=0.8)+
    xlab("Mean Complex Path Length") +
    ylab("Mean Local Clustering Coefficient") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
  scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid(Tipping_Strategy ~ Innovators, labeller = label_both ) 

```
---------------Simulation Time



--------------------------------- Mean Simple Path Length
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = MPL, y = Sim_Time, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Mean_Simple_Path_Length") +
    ylab("Sim_Time") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
  scale_y_log10()+
  scale_x_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```

--------------------------------- Mean Complex Path Length
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = MCPL, y = Sim_Time, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Mean_Complex_Path_Length") +
    ylab("Sim_Time") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
  scale_x_log10()+
  scale_y_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```


--------------------------------- Variance Node Degree
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = VD, y = Sim_Time, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Variance_Node_Degree") +
    ylab("Sim_Time") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
 # scale_x_log10()+
  scale_y_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```


--------------------------------- Mean Local Clustering Coefficient
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = MSCl, y = Sim_Time, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Mean Local Clustering Coefficient") +
    ylab("Sim_Time") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
 # scale_x_log10()+
  scale_y_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```


--------------------------------- Mean Global Clustering Coefficient
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = GCC, y = Sim_Time, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Global Clustering Coefficient") +
    ylab("Sim_Time") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
 # scale_x_log10()+
  scale_y_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```



--------------------------------- Variance Local Clustering Coefficient
```{r echo=FALSE,fig.height=15, fig.width=15, message=FALSE, warning=FALSE, results='asis'}
#df_mean$Majority_Green <- as.factor(df_mean$Majority_Green)
# "Mean_Average_Path", #Connections","Mean_Node_Degree", "Mean_Cluster_Coefficient"
df_mean %>% filter() %>%
   dplyr::sample_frac(1) %>%
ggplot(aes(x = VCCo, y = Sim_Time, shape == Tipping_Strategy, color = Tipping_Strategy)) +
    #geom_histogram(binwidth=0.01)+
      geom_point (size = 2) + 
   geom_smooth(span=0.8)+
    xlab("Variance Local Clustering Coefficient") +
    ylab("Sim_Time") + 
   #labs(title = "MPL")+
    scale_color_viridis_d()+
 # scale_x_log10()+
  scale_y_log10()+
    theme_bw()+
    theme(strip.background = element_rect(fill="black"),
          strip.text = element_text(size=12, colour="white", face = "bold"), 
          plot.title = element_text( size = 18), 
          plot.subtitle = element_text( size = 15),
          axis.title = element_text( size = 18) ) +
   facet_grid( ~ Innovators, labeller = label_both ) 

```




